Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-12-18 Manuscript/manuscript.tex
Small edits in Methods section (finished till its end)

To validate the structures of lipid bilayers, the scattering form factors and C-H bond order parameters
were calculated and compared against the experimental data as described previously~\cite{botan15,ollila16,melcr18,nmrlipids_proj4}.
%in simulations without ions were validated against NMR 
%by calculating the order parameters for the C-H bonds and against \mbox{X-ray} scattering experiments by evaluating 
%as was done in Refs.~\citenum{catte16, melcr18, nmrlipids_proj4}.
%NMR order parameters validate the structures sampled by the individual lipid molecules with atomic resolution. 
%The simulated order parameters were calculated for all C-H bonds in lipid molecules, 
%while all order paremeters in the head group and only some in the \ce{C-H} groups in tails were resolved experimentally
%(see next section and Fig.~\ref{simVSexpNOions_POPS}). 
The order parameters for each C-H bond of individual lipids in the trajectory were first averaged
over the time. Then the average over lipids was taken and the standard error of the mean of this
average was used as an error bar \cite{botan15,ollila16,nmrlipids_proj4}.

Cation binding affinity to phosphatidylcholine (PC) lipid bilayers can be evaluated using 
the order parameters of $\alpha$ and $\beta$ carbons in the lipid headgroup 
(see Fig.~\ref{simVSexpNOions_POPS} for the labeling
\todo{SAMULI: Currently the figure has only PS structure while we use PC also in this work.
We should either add also PC structure or refer to somewhere else for the labeling.}) \cite{catte16}.
According to the ''electrometer concept'' \citep{seelig87}, these order parameters decrease
proportionally to the bound charge and can therefore be used to quantify the cation binding
affinity to PC lipid bilayers. The situation is more complicated for lipid bilayers containing
PS lipids because the ion free reference state does not exist due to the counterions and additional
ions often lead to phase transitions \cite{nmrlipids_proj4,feigenson86,mattai89,roux91,roux90}
Here, we overcome these complications by comparing simulations to the experimental data measured
from POPC:POPS (5:1) mixtures with additional ions\cite{roux90}, as demonstrated in the
recent work by the NMRlipids project \cite{nmrlipids_proj4}.

@@

MD simulations of POPC:POPS lipid bilayers with different molar ratios 
and ion concentrations (\ce{K^+}, \ce{Na^+}, \ce{Ca^{2+}} and \ce{Cl^{-}})
were performed in an orthorhombic simulation box with periodic boundary conditions
using the GROMACS 2018 \cite{Abraham15} simulation package. 
%The simulated system consisted of lipids (POPC and POPS) forming a single lipid bilayer,
%an amount of water molecules comparable to the hydration levels in experiments, 
%\todo{Check this claim. SAMULI: Check discussin in the NMRlipids IV manuscript}
The simulated systems are listed in Table~\ref{tbl:sim-list} and the used parameters
in Table~\ref{tbl:mdpar}. 
\todo{SAMULI: All the simulations were ran ?? ns and the first ?? ns were omitted as
an equilibration period. Or some other description of simulation times and equlibration.}
For deposited trajectories and parameter files see 
Refs.~\citenum{ecclipids_pcps_nacl_kcl_series, ecclipids_pcps_cacl2_series, ecclipids_pcps_mixtures_counterions, 
               lipid17_nacl_kcl_series, lipid17_ff99_ions, lipid17_cacl_series}

In the reference simulations with the standard Amber force field,
we used the Lipid14 parameters~\cite{dickson14} for POPC, the Lipid17 parameters for POPS \cite{lipid17-future},
the TIP3P water model~\cite{jorgensen83}, and ion models by Dang and coworkers~\cite{smith94,chang1999,dang2006}.
The Lipid14 parameters in Gromacs format were downloaded from ?? \todo{SAMULI: Add this} and
the Lipid17 parameters were \todo{SAMULI: Describe how lipid17 parameters in Gromacs were generated.}.
The ion model by Dang and coworkers~\cite{smith94,chang1999,dang2006} was used with Amber lipids because
analysis of simulations with the default Amber ion parameters is complicated by the artificial
clustering of ions in solution \cite{nmrlipids_proj4}.
In simulations with ECC-lipids,
we used the ECC-POPC parameters~\cite{melcr18} (available at ??\todo{Add reference}) and ECC-POPS
parameteres derived in this work (section \ref{section:ecc}) together with the SPC/E~\cite{Berendsen1987}
water model and ECC-ions \cite{martinek17, kohagen16, Pluharova2014}.
The SPC/E water model is used because it lower dielectric constant is consistent with the
ECC concept \cite{leontyev11,leontyev14}.

The simulation parameters used in this work are summarized in Table~\ref{tbl:mdpar}.

@@

>>>>

To validate the structures of lipid bilayers, the scattering form factors and C-H bond order parameters
were calculated and compared against the experimental data as described previously~\cite{botan15,ollila16,melcr18,nmrlipids_proj4}.
%in simulations without ions were validated against NMR 
%by calculating the order parameters for the C-H bonds and against \mbox{X-ray} scattering experiments by evaluating 
%as was done in Refs.~\citenum{catte16, melcr18, nmrlipids_proj4}.
%NMR order parameters validate the structures sampled by the individual lipid molecules with atomic resolution. 
%The simulated order parameters were calculated for all C-H bonds in lipid molecules, 
%while all order paremeters in the head group and only some in the \ce{C-H} groups in tails were resolved experimentally
%(see next section and Fig.~\ref{simVSexpNOions_POPS}). 
The order parameters for each C-H bond of individual lipids in the trajectory were first averaged
over the time. Then the average over lipids was taken and the standard error of the mean of this
average was used as the error estimate of the mean \cite{botan15,ollila16,nmrlipids_proj4}.

Cation binding affinity to phosphatidylcholine (PC) lipid bilayers can be evaluated using 
the order parameters of $\alpha$ and $\beta$ carbons in the lipid headgroup 
(see Fig.~\ref{fig:chemstruct_pc_ps} for the labeling) \cite{catte16}.
According to the ''electrometer concept'' \citep{seelig87}, these order parameters decrease
proportionally to the bound charge and can therefore be used to quantify the cation binding
affinity to lipid bilayers. The situation is more complicated for lipid bilayers containing
PS lipids, for which there is no ion-free reference state due to the presence of counterions.
Moreover, additional ions often lead to phase transitions in such bilayers \cite{nmrlipids_proj4,feigenson86,mattai89,roux91,roux90}
Here, we overcome this complication by comparing simulations to the experimental data 
measured from POPC:POPS (5:1) mixtures, 
which are not as highly negatively charged, 
and do not ondergo phase transitions with additional ions \cite{roux90} 
as was also demonstrated in the recent work by the NMRlipids project \cite{nmrlipids_proj4}.

@@

MD simulations of POPC:POPS lipid bilayers with different molar ratios 
and ion concentrations (\ce{K^+}, \ce{Na^+}, \ce{Ca^{2+}} and \ce{Cl^{-}})
were performed in an orthorhombic simulation box with periodic boundary conditions
using the GROMACS 2018 \cite{Abraham15} simulation package. 
%The simulated system consisted of lipids (POPC and POPS) forming a single lipid bilayer,
%an amount of water molecules comparable to the hydration levels in experiments, 
%\todo{Check this claim. SAMULI: Check discussin in the NMRlipids IV manuscript}
The complete set of simulated systems is listed in Table~\ref{tbl:sim-list},
and the used simulation parameters are in Table~\ref{tbl:mdpar}. 
All simulations were ran for a minimum of $1 \, \mu$s,
and the first  $50 \,$ns were omitted as an equilibration period. 
For deposited trajectories and parameter files see 
Refs.~\citenum{ecclipids_pcps_nacl_kcl_series, ecclipids_pcps_cacl2_series, ecclipids_pcps_mixtures_counterions, 
               lipid17_nacl_kcl_series, lipid17_ff99_ions, lipid17_cacl_series}

In the reference simulations with the standard Amber force field,
we used the Lipid14 parameters~\cite{dickson14} for POPC, the Lipid17 parameters for POPS \cite{lipid17-future},
the TIP3P water model~\cite{jorgensen83}, and ion models by Dang and coworkers~\cite{smith94,chang1999,dang2006}.
The Lipid14 parameters in Gromacs format were downloaded from Ref.~\citenum{lipid14files}. 
The Lipid17 parameters were obtained from AmberTools18 \cite{amber18} 
and they were converted to Gromacs format using acpype \cite{acpype}.  
The ion model by Dang and coworkers~\cite{smith94,chang1999,dang2006} was used with Amber lipids because
analysis of simulations with the default Amber ion parameters is complicated by the artificial
clustering of ions in solution \cite{nmrlipids_proj4}.
In the simulations with ECC-lipids,
we used the ECC-POPC parameters~\cite{melcr18} (available at \cite{ECC-POPC_nacl_cacl2_files}) and 
ECC-POPS parameteres derived in this work (section \ref{section:ecc}) 
together with the SPC/E~\cite{Berendsen1987} water model and 
ECC-ions \cite{martinek17, kohagen16, Pluharova2014}.
We used the SPC/E water model as its lower dielectric constant is consistent with the
ECC concept \cite{leontyev11,leontyev14}.

@@

\begin{figure}[tb!] 
  \centering 
  \includegraphics[width=\figwidth]{../Fig/lipids_chemfig_POPC_POPS.pdf} 
  \caption{ \label{fig:chemstruct_pc_ps} 
            The chemical structure of POPC and POPS 
            including the labeling of the carbon segments
            used in the measurements of order parameteres. 
  }  
\end{figure}
